The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-13 albatros_paper.tex
HCC merged Marion map and synthesized beam figures

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
    \caption{Map of Marion Island.  The \albatros\ pathfinder antennas
      are currently installed at the \prizm\ site and at the hydro
      shack.  The black markers denote the eight coastal huts, which
      will be used for future \albatros\ antenna installations.  The
      white markers denote other available infrastructure points that
      will not be used for antennas.  \attention{Add new
        synthesized beam figure (Jon)}}
    \label{Fig:marion}
  \end{center}
\end{figure}

@@

Marion Island is a research base that is located in the southern
Indian Ocean at \ang{46;54;45}S, \ang{37;44;37}E and is operated by
the South African National Antarctic Programme.  The island lies
roughly \SI{2000}{\kilo\metre} from the nearest continental landmasses
and has an exceptionally quiet RFI
environment~\citep{2019JAI.....850004P}.  As illustrated in
\autoref{Fig:marion}, \attention{this points to the map, not the beam pattern} Marion has an area of 335~km$^2$ and can
therefore support antenna installations with $>10$-km baseline
lengths.  The main Marion base is located on the northeast side of the
island, and there are eight rest huts along the coast (Cape Davis,
Grey-headed, Kildalkey, Mixed Pickle, Repettos, Rooks, Swartkops,
Watertunnel) and one in the interior (Katedraal) that can serve as
existing infrastructure points for antenna installations.  The planned
\albatros\ installation sites include the coastal huts, but exclude
the main base and Katedraal for RFI and accessibility reasons,
respectively.  \autoref{Fig:marion} also shows the locations of the
\albatros\ pathfinder antennas that are currently installed at the
\prizm\ site and at the hydro shack.

Using the eight coastal huts, the \prizm\ site, and the hydro shack as
the nominal \albatros\ installation locations, the computed
synthesized beam is as shown in \autoref{Fig:marion}.  The beam width
at 5~MHz is roughly \SI{8}{\arcminute}, which represents over an order
of magnitude improvement in resolution over other existing
measurements.  One of the challenges in constructing an interferometer
array on Marion Island is that the rugged terrain precludes the
possibility of directly cabling and correlating antennas across large
distances.  The final \albatros\ antenna stations will therefore
operate {\it autonomously}, recording baseband data over extended
periods of time for subsequent offline correlation.  We have conducted
two enginering runs: 1) a two-element, directly correlated pathfinder
to qualitatively understand the sky signal, and 2) a single station to
test the readout and power handling technology that are required for
autonomous operation.

@@

% Two-element block diagram goes here
\begin{figure}
  \begin{center} \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Two-element \albatros\ pathfinder block diagram.
      Signals from two dual-polarzation LWA antennas are amplified by
      front-end active baluns (\attention{citation for FEE}).
      Antennas are connected via 100m coax cables to the back-end 
      readout electronics, which are housed in a Faraday cage denoted
      by the dashed box.  Each of the four antenna outputs is passed
      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes auto and cross spectra
      from and between the four inputs.  A Raspberry Pi controls the SNAP board and
      saves the data.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

@@

\attention{ALL TEXT BELOW HERE NEEDS WORK}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.6\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/marion_map/marion_map_annotated.jpg} 
        \caption{} \label{Fig:marion_map}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.39\textwidth}
      \centering
        \includegraphics[width=\linewidth]{Figures/marion_beam_huts_2020.jpg}
        \caption{} \label{Fig:marion_beam}
    \end{subfigure}
    \caption{{\bf (a)} Map of Marion Island.  The
      \albatros\ pathfinder antennas are currently installed at the
      \prizm\ site and at the hydro shack (gray markers).  The black
      markers denote the eight coastal huts, which will be used for
      future \albatros\ antenna installations.  The white markers
      denote other available infrastructure points that will not be
      used for antennas.  {\bf (b)} Synthesized beam at 5~MHz from the
      full \albatros\ array, using the existing and planned
      installation locations shown on the map.  Using an octave of
      bandwidth spanning 3.5--7~MHz, we obtain a synthesized beam with
      a full width of $\sim7'$.}\label{Fig:marion_map_beam}
\end{figure}

@@

% \begin{figure}
%   \begin{center}
%     \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
%     \caption{Map of Marion Island.  The \albatros\ pathfinder antennas
%       are currently installed at the \prizm\ site and at the hydro
%       shack.  The black markers denote the eight coastal huts, which
%       will be used for future \albatros\ antenna installations.  The
%       white markers denote other available infrastructure points that
%       will not be used for antennas.  \attention{Add new
%         synthesized beam figure (Jon)}}
%     \label{Fig:marion}
%   \end{center}
% \end{figure}

@@

Marion Island is a research base that is located in the southern
Indian Ocean at \ang{46;54;45}S, \ang{37;44;37}E and is operated by
the South African National Antarctic Programme.  The island lies
roughly \SI{2000}{\kilo\metre} from the nearest continental landmasses
and has an exceptionally quiet RFI
environment~\citep{2019JAI.....850004P}.  As illustrated in
\autoref{Fig:marion_map}, Marion has an area of 335~km$^2$ and can
therefore support antenna installations with $>10$-km baseline
lengths.  The main Marion base is located on the northeast side of the
island, and there are eight rest huts along the coast (Cape Davis,
Grey-headed, Kildalkey, Mixed Pickle, Repettos, Rooks, Swartkops,
Watertunnel) and one in the interior (Katedraal) that can serve as
existing infrastructure points for antenna installations.  The planned
\albatros\ installation sites include the coastal huts, but exclude
the main base and Katedraal for RFI and accessibility reasons,
respectively.  \autoref{Fig:marion_map} also shows the locations of
the \albatros\ pathfinder antennas that are currently installed at the
\prizm\ site and at the hydro shack.

Using the eight coastal huts, the \prizm\ site, and the hydro shack as
the nominal \albatros\ installation locations, the computed
synthesized beam is as shown in \autoref{Fig:marion_beam}.  The beam
width at 5~MHz is roughly \SI{7}{\arcminute}, which represents over an
order of magnitude improvement in resolution over other existing
measurements.  One of the challenges in constructing an interferometer
array on Marion Island is that the rugged terrain precludes the
possibility of directly cabling and correlating antennas across large
distances.  The final \albatros\ antenna stations will therefore
operate {\it autonomously}, recording baseband data over extended
periods of time for subsequent offline correlation.  We have conducted
two engineering runs: 1) a two-element, directly correlated pathfinder
to qualitatively understand the sky signal, and 2) a single station to
test the readout and power handling technology that are required for
autonomous operation.

% \begin{figure}
%   \begin{center}
%     \includegraphics[width=0.7\linewidth]{Figures/marion_beam_huts_2020.pdf}
%     %/Users/sievers/hirax/outriggers/marion_beam_huts_2020.pdf
%     \caption{Synthesized beam at 5 MHz from the full \albatros\ array.
%       We use an octave of bandwidth (3.5 to 7 MHz), and find the
%       ensuing synthesized beam has a FWHM of about 7 arcminutes.}
%     \label{Fig:beam}
%   \end{center}
% \end{figure}

@@

\begin{figure}
  \begin{center} \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Two-element \albatros\ pathfinder block diagram.
      Signals from two dual-polarzation LWA antennas are amplified by
      front-end active baluns (\attention{citation for FEE}).
      Antennas are connected via 100m coax cables to the back-end 
      readout electronics, which are housed in a Faraday cage denoted
      by the dashed box.  Each of the four antenna outputs is passed
      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes auto and cross spectra
      from and between the four inputs.  A Raspberry Pi controls the SNAP board and
      saves the data.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

@@
